\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-21 paper.tex
3.1 and others

\begin{document}
\title{\bf $\mathsf{TEDAT}$: Boosting Bandwidth Availability Over Inter-DC WAN}

@@

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{TEDAT}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{TEDAT}$ is able to maximize revenue when network fails.
%$\mathsf{TEDAT}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{TEDAT}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{TEDAT}$ over inter-DC WAN.
The three core components of  $\mathsf{TEDAT}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{TEDAT}$ can speed up the online admission control by 30 $\times$ at the expense of a 5\% higher rejection ratio. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{TEDAT}$ can meet the bandwidth availability SLAs for 40\% more demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{TEDAT}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{TEDAT}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Secondly, we design $\mathsf{TEDAT}$,

@@

$\mathsf{TEDAT}$ is composed of three core components, i.e., admission control, traffic scheduling and failure recovery. 

@@

%$\mathsf{TEDAT}$ framework contains three parts, i.e., admission control, online scheduling and failure recovery.

@@

%Compared with TEAVAR \cite{Teavar},  $\mathsf{TEDAT}$ can achieve a more reasonable balance between network utilization and availability when network resource is sufficient, and guarantee diverse availability targets of services when network resource is inadequate.
%$\mathsf{TEDAT}$  also pre-computes backup allocation across each tunnel to maximize revenue when a link fails.

@@

%Therefore, $\mathsf{TEDAT}$ can maintain profit even network fails without too much extra bandwidth headroom.

@@

%$\mathsf{TEDAT}$ is motivated by the observation that empirical link failure traces available to the network operators allow us to estimate link failure probabilities and to reason availability under different network states.

@@

%%Operators actually have empirical link failures traces of inter-DC WAN and $\mathsf{TEDAT}$ can estimate the failure probability of links from these data.

@@

%%We define $\mathsf{TEDAT}$ optimization problem which aims to maximize total profit subject to bandwidth-based availability demands. 
%We define $\mathsf{TEDAT}$ optimization problem to maximize SLA-aware total profit subject to bandwidth-based availability demands.
%$\mathsf{TEDAT}$ problem is a 0-1 mixed-integer linear program and  it is proven to be NP-hard.
%$\mathsf{TEDAT}$  aims for bandwidth-based availability provision, where a set of demands on transmission bandwidth in inter-DC WAN should be satisfied with their expected probabilities.
%%$\mathsf{TEDAT}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on bandwidth-based availability. 

@@

% $\mathsf{TEDAT}$ defines Weighted Availability Profit Maximization (WAPM) problem which optimizes applications' total availability profit.
%Input of $\mathsf{TEDAT}$ contains two parts: (1) Network states and its corresponding probability reasoned from the empirical data of WAN link/node failure; (2) Application level traffic matrix which is composed of bandwidth and availability demands.

@@

%$\mathsf{TEDAT}$ optimizes the total availability profit.

@@

%$\mathsf{TEDAT}$ problem is a 0-1 mixed-integer linear program and we prove it is NP-hard.

@@

%Under $\mathsf{TEDAT}$, services are very likely free from congestion, while maintaining high network utilization.
%Compared with other TE schemes (see $\S$\ref{relate}),  it achieves better tradeoff between network utilization and availability.

Thirdly, 
we implement $\mathsf{TEDAT}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{TEDAT}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{TEDAT}$ can 
(1) speed up the online admission control by 30 $\times $ at the expense of a rejection ratio that is 5\% higher than the optimal strategy;
(2) meet the bandwidth availability SLAs for 40\% more demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{TEDAT}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under TEDAT, links can maintain high utilization.

%In summary, we make four key contributions:
%
%\begin{itemize}
%\item We analyze deficiency of state-of-the-art availability traffic engineering schemes and  advocate bandwidth-based availability traffic engineering.
%\item We propose $\mathsf{TEDAT}$
%a novel TE framework that defines WAPM problem to maximize total profit subject to application availability demands with network failure probability.
%We prove WAPM is NP-hard and propose a heuristic algorithm to solve it efficiently.
%\item  We design an SDN-based system named $\mathsf{Dionysus}$ which works in the centralized way to implement  $\mathsf{TEDAT}$.
%\item We evaluate the performance of $\mathsf{TEDAT}$ in both real trace driven simulation as well as real testbed. 
%Evaluation  results show  $\mathsf{TEDAT}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands than TEAVAR\cite{Teavar}, SMORE\cite{SMORE}, SWAN\cite{swan} and FFC\cite{FFC}, respectively.
%\end{itemize}

@@

\begin{figure*}[t]
\centering
\subfigure[Capacity and failure probability]{
\includegraphics[width=0.24\textwidth]{fig/motivation-link.pdf}}
\subfigure[FFC (with one failure) ]{
\includegraphics[width=0.24\textwidth]{fig/motivation-ffc.pdf}}
\subfigure[TEAVAR]{
\includegraphics[width=0.24\textwidth]{fig/motivation-teavar.pdf}}
\subfigure[ $\mathsf{TEDAT}$]{
\includegraphics[width=0.24\textwidth]{fig/motivation-hate.pdf}}
\caption{A simple example where user1 (red) requires 6Gbps bandwidth for at least 99\% time and user2 (blue) requires 12Gbps bandwidth for at least 90\% time, both from DC1 to DC4. }%Link capacity is 10Gbps everywhere. Neither user gets enough bandwidth or availability guarantees under FFC or TEAVAR.  Both users are in line with their SLAs under $\mathsf{TEDAT}$. }
\label{motivatio_fig}
\end{figure*}

@@

\subsection{A motivating example for $\mathsf{TEDAT}$}
Now we use a simple example to illustrate why existing traffic engineering algorithms cannot 
meet the heterogeneous bandwidth availability demands well. The toy topology we use is depicted 
in Figure \ref{motivatio_fig}(a), where there are 4 data centers and the links connecting them 
are annotated with their corresponding capacities and failure probabilities. Suppose we have two 
bandwidth demands for inter-DC transmission from DC1 to DC4, i.e., user1 (red) requires 6Gbps bandwidth 
with at least 99\% availability, and user2 (blue) requires 12Gbps bandwidth with at least 90\% availability. 
There are two paths from DC1 to DC4, i.e., DC1$\to$ DC2 $\to$ DC4, and DC1 $\to$ DC3 $\to$ DC4, whose available probabilities are $(1-4\%) \times (1-0.0001\%)=95.999904\%$ and $(1-0.1\%) \times (1-0.0001\%) = 99.8999001\%$, respectively. We apply FFC \cite{FFC} and TEAVAR \cite{Teavar}, two latest WAN traffic engineering schemes that take network failures into account, to this scenario.

@@

\textbf{Our approach:}
%$\mathsf{TEDAT}$ exploits network failure probability and attempts to satisfy applications'  bandwidth-based availability demands.
Taking into account the diverse link failure probabilities and user bandwidth availability demands, 
Figure \ref{motivatio_fig}(d) shows a better bandwidth allocation, 
where user1 can get 6Gbps over 99.8999001\% time (via the lower path that has a lower failure probability) and user2 can get 12Gbps over 95.999904\% time (via both the upper and the lower path), 
satisfying both of their bandwidth demands.

%The minimal bandwidth demands of applications are able to be met with high probability under $\mathsf{TEDAT}$.
%Low failure probability links are fully utilized to satisfy the high availability demands of applications.
%We elaborate the details of $\mathsf{TEDAT}$ in the following section.

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{TEDAT}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
\hline
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\multirow{3}{*}{$d_i=(\mathbf{b}_i, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b}_i$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b}_i$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
\hline
$D, D_a$ &\multicolumn{6}{|l}{the set of arrived demands and admitted demands}\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$d_{ik}$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

\section{The $\mathsf{TEDAT}$ framework}\label{HATE}
In this section, we discuss the details of $\mathsf{TEDAT}$, which contains three parts, i.e., admission control, traffic scheduling and failure recovery, using notations summarized in Table \ref{Notation}. 
The framework intends to achieve the following objectives: 
 \begin{itemize}
\item \textbf{High admission ratio and low admission latency:}  
  Bandwidth availability demands might arrive at anytime. 
  The system should be able to efficiently accommodate as many BA demands as possible under the constraint of network capacity and failure probabilities, as this would increase service agility and bring more revenue. %availability and bandwidth targets.
\item \textbf{High availability for allocated bandwidth:}
The system should be able to optimize its achieved availability in a probabilistic manner, 
as this would, in the long term, reduce potential penalties (i.e., refund due to SLA violations) and retain a good reputation. This can be achieved by making a good match between demands on higher availability and paths with low failure probability.
%make services with stringent availability requirements (e.g., 99.999\%) pass links with high reliability.
%Therefore, their bandwidth demands can be guaranteed with high probability.
\item \textbf{Automatic and economical failure recovery:}
If any link failure really happens, the system should reroute traffic away from that link, 
while minimizing any possible collateral damage to normal traffic, i.e., congestion and lower bandwidth availability due to rerouting.
%\item \textbf{ \& scalability:}
%
\end{itemize}

\subsection{Abstraction of bandwidth availability demands}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a tenant could be a customer who launches multiple virtual private clouds over  multiple DCs in public clouds (e.g., Amazon AWS) or could be a service team who launches multiple VM instances in private clouds (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
Services have different bandwidth demands as well as availability targets.
However, there exists no interface for tenants to specify them.
We now present $\mathsf{TEDAT}$ 's availability abstraction, which aims to guarantee the bandwidth-based availability of services.

\textbf{BA demand model:}
We model the inter-DC WAN as a  graph $G=(V,E)$,  where $V$ and $E$ are the nodes and link sets.
Each link $e\in E$ is associated with a link capacity $c_e$ (e.g., in bps).
DC pair set is $K$ and  $\beta_j$ presents the desired availability target  of service $j \in J$.
Each tenant's demand can be presented as a tuple $\{\alpha, \theta, \delta, \gamma, \mu\}$,
where $\alpha$ and $\delta$ are the arrival and departure of the demand, $\gamma$ denotes the service type and $\theta =\{d_{1}, d_{2}, ...,d_{K} \}$ presents bandwidth over each node pair.
%We assume one tenant can only start one service and if a tenant wants to boot multiple services, we can use multiple tuples to describe it.
Service providers will offer refunding for any violating availability targets (see $\S$\ref{background}) and we use $\mu$ to denote the penalty.
%The system should reserve enough bandwidth to guarantee all \textit{admitted} requests' availability demands.
%When all services'  \textit{achieved} bandwidth-based availability are larger than their corresponding desired availability target, the system is able to accommodate this service request, otherwise, the request will be denied.

>>>>

\begin{document}
\title{\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN}

@@

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{BATE}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{BATE}$ is able to maximize revenue when network fails.
%$\mathsf{BATE}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{BATE}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{BATE}$ over inter-DC WAN.
The three core components of  $\mathsf{BATE}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{BATE}$ can speed up the online admission control by 30 $\times$ at the expense of a 5\% higher rejection ratio. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{BATE}$ can meet the bandwidth availability SLAs for 40\% more demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{BATE}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{BATE}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Secondly, we design $\mathsf{BATE}$,

@@

$\mathsf{BATE}$ is composed of three core components, i.e., admission control, traffic scheduling and failure recovery. 

@@

%$\mathsf{BATE}$ framework contains three parts, i.e., admission control, online scheduling and failure recovery.

@@

%Compared with TEAVAR \cite{Teavar},  $\mathsf{BATE}$ can achieve a more reasonable balance between network utilization and availability when network resource is sufficient, and guarantee diverse availability targets of services when network resource is inadequate.
%$\mathsf{BATE}$  also pre-computes backup allocation across each tunnel to maximize revenue when a link fails.

@@

%Therefore, $\mathsf{BATE}$ can maintain profit even network fails without too much extra bandwidth headroom.

@@

%$\mathsf{BATE}$ is motivated by the observation that empirical link failure traces available to the network operators allow us to estimate link failure probabilities and to reason availability under different network states.

@@

%%Operators actually have empirical link failures traces of inter-DC WAN and $\mathsf{BATE}$ can estimate the failure probability of links from these data.

@@

%%We define $\mathsf{BATE}$ optimization problem which aims to maximize total profit subject to bandwidth-based availability demands. 
%We define $\mathsf{BATE}$ optimization problem to maximize SLA-aware total profit subject to bandwidth-based availability demands.
%$\mathsf{BATE}$ problem is a 0-1 mixed-integer linear program and  it is proven to be NP-hard.
%$\mathsf{BATE}$  aims for bandwidth-based availability provision, where a set of demands on transmission bandwidth in inter-DC WAN should be satisfied with their expected probabilities.
%%$\mathsf{BATE}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on bandwidth-based availability. 

@@

% $\mathsf{BATE}$ defines Weighted Availability Profit Maximization (WAPM) problem which optimizes applications' total availability profit.
%Input of $\mathsf{BATE}$ contains two parts: (1) Network states and its corresponding probability reasoned from the empirical data of WAN link/node failure; (2) Application level traffic matrix which is composed of bandwidth and availability demands.

@@

%$\mathsf{BATE}$ optimizes the total availability profit.

@@

%$\mathsf{BATE}$ problem is a 0-1 mixed-integer linear program and we prove it is NP-hard.

@@

%Under $\mathsf{BATE}$, services are very likely free from congestion, while maintaining high network utilization.
%Compared with other TE schemes (see $\S$\ref{relate}),  it achieves better tradeoff between network utilization and availability.

Thirdly, 
we implement $\mathsf{BATE}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{BATE}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{BATE}$ can 
(1) speed up the online admission control by 30 $\times $ at the expense of a rejection ratio that is 5\% higher than the optimal strategy;
(2) meet the bandwidth availability SLAs for 40\% more demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{BATE}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under BATE, links can maintain high utilization.

%In summary, we make four key contributions:
%
%\begin{itemize}
%\item We analyze deficiency of state-of-the-art availability traffic engineering schemes and  advocate bandwidth-based availability traffic engineering.
%\item We propose $\mathsf{BATE}$
%a novel TE framework that defines WAPM problem to maximize total profit subject to application availability demands with network failure probability.
%We prove WAPM is NP-hard and propose a heuristic algorithm to solve it efficiently.
%\item  We design an SDN-based system named $\mathsf{Dionysus}$ which works in the centralized way to implement  $\mathsf{BATE}$.
%\item We evaluate the performance of $\mathsf{BATE}$ in both real trace driven simulation as well as real testbed. 
%Evaluation  results show  $\mathsf{BATE}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands than TEAVAR\cite{Teavar}, SMORE\cite{SMORE}, SWAN\cite{swan} and FFC\cite{FFC}, respectively.
%\end{itemize}

@@

\begin{figure*}[t]
\centering
\subfigure[Capacity and failure probability]{
\includegraphics[width=0.24\textwidth]{fig/motivation-link.pdf}}
\subfigure[FFC (with one failure) ]{
\includegraphics[width=0.24\textwidth]{fig/motivation-ffc.pdf}}
\subfigure[TEAVAR]{
\includegraphics[width=0.24\textwidth]{fig/motivation-teavar.pdf}}
\subfigure[ $\mathsf{BATE}$]{
\includegraphics[width=0.24\textwidth]{fig/motivation-hate.pdf}}
\caption{A simple example where user1 (red) requires 6Gbps bandwidth for at least 99\% time and user2 (blue) requires 12Gbps bandwidth for at least 90\% time, both from DC1 to DC4. }%Link capacity is 10Gbps everywhere. Neither user gets enough bandwidth or availability guarantees under FFC or TEAVAR.  Both users are in line with their SLAs under $\mathsf{BATE}$. }
\label{motivatio_fig}
\end{figure*}

@@

\subsection{A motivating example for $\mathsf{BATE}$}
Now we use a simple example to illustrate why existing traffic engineering algorithms cannot 
meet the heterogeneous bandwidth availability demands well. The toy topology we use is depicted 
in Figure \ref{motivatio_fig}(a), where there are 4 data centers and the links connecting them 
are annotated with their corresponding capacities and failure probabilities. Suppose we have two 
bandwidth demands for inter-DC transmission from DC1 to DC4, i.e., user1 (red) requires 6Gbps bandwidth 
with at least 99\% availability, and user2 (blue) requires 12Gbps bandwidth with at least 90\% availability. 
There are two paths from DC1 to DC4, i.e., DC1$\to$ DC2 $\to$ DC4, and DC1 $\to$ DC3 $\to$ DC4, whose available probabilities are $(1-4\%) \times (1-0.0001\%)=95.999904\%$ and $(1-0.1\%) \times (1-0.0001\%) = 99.8999001\%$, respectively. We apply FFC \cite{FFC} and TEAVAR \cite{Teavar}, two latest WAN traffic engineering schemes that take network failures into account, to this scenario.

@@

\textbf{Our approach:}
%$\mathsf{BATE}$ exploits network failure probability and attempts to satisfy applications'  bandwidth-based availability demands.
Taking into account the diverse link failure probabilities and user bandwidth availability demands, 
Figure \ref{motivatio_fig}(d) shows a better bandwidth allocation, 
where user1 can get 6Gbps over 99.8999001\% time (via the lower path that has a lower failure probability) and user2 can get 12Gbps over 95.999904\% time (via both the upper and the lower path), 
satisfying both of their bandwidth demands.

%The minimal bandwidth demands of applications are able to be met with high probability under $\mathsf{BATE}$.
%Low failure probability links are fully utilized to satisfy the high availability demands of applications.
%We elaborate the details of $\mathsf{BATE}$ in the following section.

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in the set of s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
\hline
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\multirow{3}{*}{$d_i=(\mathbf{b}_i, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b}_i$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b}_i$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
\hline
$D, D_a$\footnote{$D_a$ will update every time slot and an admitted demand will be removed if it finishes.} &\multicolumn{6}{|l}{the set of arrived demands and admitted demands}\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$d_{ik}$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

\section{$\mathsf{BATE}$ framework}\label{HATE}
In this section, we discuss the details of $\mathsf{BATE}$, which contains three parts, i.e., admission control, traffic scheduling and failure recovery, using notations summarized in Table \ref{Notation}. 
The framework intends to achieve the following objectives: 
 \begin{itemize}
\item \textbf{High admission ratio and low admission latency:}  
  Bandwidth availability demands might arrive at anytime. 
  The system should be able to efficiently accommodate as many BA demands as possible under the constraint of network capacity and failure probabilities, as this would increase service agility and bring more revenue. %availability and bandwidth targets.
\item \textbf{High availability for allocated bandwidth:}
The system should be able to optimize its achieved availability in a probabilistic manner, 
as this would, in the long term, reduce potential penalties (i.e., refund due to SLA violations) and retain a good reputation. This can be achieved by making a good match between demands on higher availability and paths with low failure probability.
%make services with stringent availability requirements (e.g., 99.999\%) pass links with high reliability.
%Therefore, their bandwidth demands can be guaranteed with high probability.
\item \textbf{Automatic and economical failure recovery:}
If any link failure really happens, the system should reroute traffic away from that link, 
while minimizing any possible collateral damage to normal traffic, i.e., congestion and lower bandwidth availability due to rerouting.
%\item \textbf{ \& scalability:}
%
\end{itemize}

\subsection{Abstraction of bandwidth availability demands}
%Recently, deploying multiple virtual private clouds over public clouds (e.g., Amazon AWS) or deploying multiple services over private clouds (e.g., Google internal DCs) is becoming  a common practice for content providers.
%Tenants could deploy diverse service instances over Inter-DC WAN.
In reality, a customer could be a tenant who launches multiple virtual private clouds over  multiple DCs in public clouds (e.g., Amazon AWS) or could be a service team who launches multiple VM instances in private clouds (e.g., Google internal DCs).
%The cloud providers are providing many services and each service contains numerous instances across geo-distributed data centers.
%For example, a common practice is running MapReduce operations across geo-distributed data centers and many connections from mappers to reducers are maintained.
%Services have different bandwidth demands as well as availability targets.
However, there exists no interface for tenants to specify bandwidth availability.
We now present $\mathsf{BATE}$ 's availability abstraction.
